Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
Adds Malacology subsection to Cluster State Mgmt

% straw man example
Keeping track of the state of a distributed system is an essential part of any 
successful service and a necessary component in order to diagnose and detect 
failures, when they occur. In the case of Ceph, a consistent view of cluster 
state among server daemons and clients is critical
to provide strong consistency guarantees to clients. Ceph maintains cluster
state information in per-subsystem ``maps'' (e.g. OSD map, MDS map) that
record membership and status information. A PAXOS-based monitoring service is
responsible for integrating state changes into cluster maps, and responding to
requests from out-of-date clients. As a fundamental building block of many
system designs, consensus abstractions such as PAXOS are a common technique
for maintaining consistent data versions, and are a useful system to expose.

While Ceph does not expose this service directly, it does allow limited use by
clients through a key-value service intended for low-volume, small size
configuration information. Unfortunately, while a key-value service is
generally useful, it doesn't provide many of the useful services hidden within
the monitoring framework that would be required for applications with more
demanding requirements.

\paragraph*{Malacology:} Malacology exposes the monitoring service in two ways. 
First, Malacology APIs for object storage (\S\ref{active-storage}) and the MDS 
(\S\ref{malacology:mds}) have functions available to them that allow them to 
store application-specific data in the highly-available, consistent store 
associated to the Ceph monitors. As mentioned
Map modification for propogation of state. We allow applications to augment
these data structures with application-specific metadata. In order to keep the
size of these data structures small application state may be stored elsewhere
and the references stored within the data structure.

>>>>

% straw man example
Keeping track of the state of a distributed system is an essential part of any 
successful service and a necessary component in order to diagnose and detect 
failures, when they occur. In the case of Ceph, a consistent view of cluster 
state among server daemons and clients is critical to provide strong consistency 
guarantees to clients. Ceph maintains cluster state information in per-subsystem 
``maps'' (e.g. OSD map, MDS map) that record membership and status information. 
A PAXOS-based monitoring service (termed, the Monitor) is responsible for 
integrating state changes into cluster maps, responding to requests from 
out-of-date clients and synchronizing members of the cluster whenever there is a 
change in a map so that they all observe the same system state. As a fundamental 
building block of many system designs, consensus abstractions such as PAXOS are 
a common technique for maintaining consistent data versions, and are a useful 
system to expose.

The default behavior of the monitor can be seen as a PAXOS-based notification 
system, similar to the one introduced in~\cite{burrows_chubby_2006}, allowing 
clients to identify when new values (termed epochs in Ceph) are associated to 
given maps. While Ceph does not expose this service directly, it does allow 
limited use by clients through a key-value service intended for low-volume, 
small size read-only configuration information. While a key-value service is 
generally useful, it doesn't provide many of the useful services hidden within 
the monitoring framework that would be required for applications with more 
demanding requirements, such as creating arbitrary maps or associating 
application-specific logic that can be executed for particular maps (or values 
in a map).

\paragraph*{Malacology:} Malacology exposes Ceph's PAXOS-based monitoring 
service in two ways. First, a Lua VM is embedded in the monitors that implements 
a generic API for creating maps and associating arbitrary data to them. This API 
also allows clients to specify small snippets of Lua code that can be executed 
on monitors. As a consequence of this, applications can define simple but useful 
domain-specific logic to the PAXOS quorum, such as authorization control (just 
specific clients can write new values) or to trigger actions based on specific 
values (e.g. sanitize values). Since the monitor is intended to be out of 
high-performance I/O paths, a general guideline is to make use of this 
functionality infrequently and to assign small values to maps. Malacology itself 
makes use of this functionality to version object interfaces defined in OSDs 
(\S\ref{active-storage}) and load balancing policies in MDSs 
(\S\ref{malacology:mds}).
